An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-28 paper/paper.tex
Paper: Add example of DHT lookup algorithm (Kademlia)

\hyphenation{MTA SZTAKI}

@@

% TODO make title page look nicer
\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[1.75cm]
\LARGE{\textsc {\textbf{Improving the Speed of Peer to Peer Backup Systems with BitTorrent}}}\\[0.5cm]
\vspace{0.25cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.75cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{1cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\vspace{.25cm}
\large{\textbf{Mih\'aly H\'eder}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
% TODO adjectives
% TODO format this section better
Mih\'aly H\'eder, our SZTAKI Project Advisor, for his advice, insight, expertise, and bottomless teapot.\\

\noindent G\'abor S\'ark\"ozy, our WPI Project Advisor, for his guidance, encouragement, and editorial skills. \\

@@

Although they have not gained much popularity, peer to peer (P2P) file backup systems have been created and studied by researchers for over a decade. These systems do not suffer from the aforementioned drawbacks of centralized systems; they are free to use, limited in storage only by the user, and do not require a trusted central entity. Instead of backing up their data to a server, peers back up their data to \textit{each other}. However, abandoning the centralized server model in favor of a distributed one brings with it new problems that must be addressed before wide-spread adoption can be expected. Research in this area has focused on topics such as handling node churn\footnote{Node churn refers to the continuous arrival and departure of nodes in a P2P network. See Sections  \ref{subsec:PeertoPeerNetworks} and \ref{sec:churn} for more detail.} \cite{ChurnResilient}, efficient routing algorithms \cite{Kademlia}, and minimizing bandwidth \cite{PeerStore}.

We have designed and implemented a new P2P backup system, called \mbox{BTBackup}, that improves the speed of backing up and recovering data. Our primary contribution, and the technology responsible for faster file backup and recovery, is the way in which we handle data transfer: BitTorrent Sync, a new synchronization application created by BitTorrent, Inc. BitTorrent Sync uses a modified version of the BitTorrent protocol \cite{BTSyncFAQ} in order to quickly synchronize files between groups of peers. This protocol is especially effective at transferring large files, which makes its use perfect for the domain of P2P file backup. By leveraging BitTorrent Sync, we take advantage of BitTorrent's ability to better utilize a peer's bandwidth by downloading from multiple sources at once. This is in contrast to other P2P backup systems, which directly download from one source at a time. Our approach takes advantage of the fact that P2P backup systems require data replication, the act of inserting several redundant copies of data into the network, to combat node churn. We view the set of nodes storing replications for a given file as a BitTorrent swarm, allowing us to use the BitTorrent protocol without additional overhead.

A secondary contribution of our research is the testing infrastructure we have designed. We created test scenarios to (1) measure the extent to which BitTorrent increases data backup and recovery transfer speeds, and (2) ensure our system is a feasible backup solution under realistic conditions. To test the former, we measured the rates of data transfer over time when backing up 1 GB of data. In order to see the effects filesize has on speed, we ran this test thrice: once with one 1GB file, once with ten 100MB files, and once with one hundred 10MB files. To test the latter, we created a test scenario that simulated usage of our system in a realistic environment. Each instance of this scenario created 100 peers on a network using MTA SZTAKI's cloud computing environment: SZTAKI Cloud. Specifically, this scenario measured the effects of node churn, or the rate at which nodes enter and leave the network, on our system. Since our system handles churn by moving replicas from unavailable nodes to available ones, we measure how much extra network traffic is generated to see the effects of churn. We take this measurement by running a test instance with no churn, and then running another one with churn. To provide a realistic setting, we had each peer limit their download and upload speeds to values that are based off of worldwide Internet bandwidth statistics.

After running our tests, we found that BitTorrent performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that \emph{larger but fewer files are handled more efficiently than a greater number of smaller files}, given the same amount of total data. We also determined that our system handles node churn well: given a rate of churn modeled off of the average Internet user, \emph{peers can expect to replace a replica every 11 days on average}. Our final and most important result is that \emph{our system was able to achieve data backup and recovery rates up to \~300\% quicker than the rates that could be realistically achieved in traditional backup systems.}

@@

\subsection{Peer to Peer Networks} \label{subsec:PeertoPeerNetworks}

@@

\subsection{Fairness} \label{sec:BackgroundFairness}
Another aspect of P2P backup systems is fairness between peers. Peers need to be storing an amount of data proportional to the amount that they are backing up to other peers. This can be challenging to enforce, because untrustworthy peers can attempt to game the system to obtain free backup storage. For example, consider a simple system where each peer must offer to store the same amount of data that they back up on other peers. A peer could claim that all of the storage space that it should be offering is being used by other peers, while in reality the peer has not taken in any other peer's data. It is clear that a mechanism needs to be built into the system that ensures that peers store the data of each other.

@@

For every file a peer wishes to back up, it must find a predetermined number of nodes that can store the file. To ensure an even distribution of responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated; the DHT provides the functionality to find the node whose ID is \textit{closest} to the randomly generated bitstring, for the overlay network's given definition of closeness. The peer then gets the metadata record for the candidate node from the DHT. From the metadata record, the peer can calculate if the candidate node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in Section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the candidate node does not have too many blacklisters. If the candidate node meets both requirements, the peer chooses it to store a replica and uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

\section{Fairness} \label{sec:Fairness}
% TODO we say "if n backups", but also refer to each backup as a "replica". we should be consistent. where else do we do this? ctrl-f replica
To ensure fairness (see Section \ref{sec:BackgroundFairness} for background information), each node must contribute storage space proportional to the amount that they are backing up. Since a peer will have replicas of its file stored on multiple nodes, the amount of space that a peer offers\footnote{That is, offers to store when it assumes the role of a node.} must be much larger than the amount of unique data that it is backing up. If $n$ backups are maintained for each file and $\mathcal{F}$ represents the set of files that a peer backs up, the total amount of space $t$ that the peer must offer can be expressed as:
\begin{equation}
t=n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i)
\end{equation}
There exists one problem with this mechanism: when the network first starts up, no peer has created any backups, so no one is obligated to store data for other peers. To solve this, our system requires that each peer is obligated to take at least $s$ bytes of data from other peers, regardless of how much data it has backed up. To include this, $t$ can be reexpressed as:
\begin{equation}
t=max(s,n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i))
\end{equation}
Let $a$ be the amount of data a node is currently storing, and $z$ be the size of a file a peer is trying to back up. When the peer finds a candidate node with $t - a > z$, it can choose that node as a replication site, knowing that it is obligated to accept the data.

@@

% TODO clarify that we are actually only testing 1 variable here, chunk size
In this scenario, we tested how our system handles a constant amount of data spread out across a varying number of files. We run this test for three reasons. First, it allows us to test the capabilities of BitTorrent Sync in handling a large number of backups. From the data gathered here, it is possible to determine how well BitTorrent Sync would scale for use in a production system, where thousands of users could each be backing up thousands of files of varying sizes. Second, it allows us to measure the performance of BitTorrent against different file sizes. Since the use case for BitTorrent is typically downloading large files, it is important to determine whether or not our system will perform well when users try to backup many small files, should it be used in a production environment. Third, it will demonstrate the ability of our system to backup and recover files faster than if they were transferred by a direct download protocol.

@@

In addition to giving us insight into the effects file size and the number of files has on the speed of data backup, we used this test scenario to determine the extent that BitTorrent increases the data transfer rate of file backup and recovery.

@@

\subsection{Upload Speed of Data Backup} \label{subsec:UploadSpeedofDataBackup}

@@

As with Figure \ref{fig:NodeRecoverySpeed}, we believe the interval of time at the start of the test with no activity is due to BitTorrent Sync indexing the 1 GB file before it can transfer it.

Table \ref{tab:UploadBackupSpeed} contains statistics about the upload speeds of each entity. Knowing that each entity contributes to the backup process, we can sum the average speeds of each to find the total average speed of backing up the data: 8608.26 kB/s. Compared to the peer's upload speed of 2768.05 kB/s, the performance of our system was 310.98\% faster.\footnote{If we look at the median values instead of the mean values, our system was $\dfrac{5040.17 \text{ kB/s}}{2268.65 \text{ kB/s}} = 222.17\%$ faster.} We were able to achieve this speed increase by using BitTorrent as the data transfer protocol in our system, effectively parallelizing the backup.

% TODO center by adjusting margins around table
\begin{table}
\begin{center}
    \begin{tabular}{| l | l | l | l | l | l | l |}
    \hline
    & Node 1 & Node 2 & Node 3 & Node 4 & Node 5 & Peer \\ \hline
    Mean & 1500.61 & 1094.83 & 1347.10 & 1240.98 & 656.69 & 2768.05\\ \hline
    Standard Deviation & 1815.66 & 1342.76 & 1645.63 & 1648.66 & 896.84 & 2512.48 \\ \hline
    Median & 757.55 & 585.35 & 757.56 & 480.7 & 190.36 & 2268.65 \\ \hline
    Max & 9141.97 & 7399.65 & 11195.35 & 8950.34 & 6252.98 & 9902.18 \\ \hline
    \end{tabular}
    \caption{Upload speed statistics of each entity in a 1 GB transfer (in kB/s)}
    \label{tab:UploadBackupSpeed}
\end{center}
\end{table}

\section{Effects of Churn} \label{sec:EffectsofChurn}

@@

Section \ref{subsec:UploadSpeedofDataBackup} showed that our system lessens the Peer's load of backing up a file by distributing the task to the nodes as well. This has the side effect of speeding up the backup process, because nodes upload the data they have at a given time to each other, better utilizing their download bandwidth. Our experiment showed that the speed increase could be upwards of 300\%. It is important to consider the number of replicas per file here, because the replica count that is maintained affects the speed and bandwidth usage of the backup and restore procedures. As the number of replicas per file increases, more traffic must be generated to create and maintain those replicas, but the download speed when recovering will be greatly improved. Of course, the maximum recovery speed is limited by the peer's download bandwidth.

Section \ref{sec:EffectsofChurn} explained that, in the presence of an average amount of churn, the average peer would need to make a new replica of any given file every 11 days. This time interval is derived by taking the average amount of time between the creation of replicas in our test instance and scaling that number based on the scaling factor that we used for the entire test instance.

@@

To test whether or not our system provided an increase in file transfer speeds, in addition to providing solutions for the other challenges of P2P backup systems, we implemented a prototype of our system and tested it on a virtualized, 100 node network using MTA SZTAKI's cloud computing system. We found that it was able to handle node churn with a reasonable amount of overhead in network traffic, requiring the replacement of a replica every 11 days. More importantly, however, we found that our system allowed for a \~300\% improvement in both file backup and restoration speeds. This would not be possible if these data transfers were only between a user and some other entity, whether it is the service provider in a centralized backup system or a single peer in another P2P backup system.

@@

@@

\bibitem{dropboxusers} https://www.dropbox.com/news/company-info
\bibitem{oneddriveusers} http://blog.onedrive.com/over-250m-people-using-skydrive/

\bibitem{ChurnResilient} S. Legtchenko, S. Monnet, P. Sens, G. Muller, Churn-Resilient Replication Strategy for Peer-to-Peer Distributed Hash-Tables
\bibitem{Kademlia} P. Maymounkov, D. Mazi\`eres, Kademlia: A Peer-to-Peer Information System Based on the XOR Metric

\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, pStore: A Secure Peer-to-Peer Backup System
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan, PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan, Storage and Search in Dynamic Peer-to-Peer Networks
\bibitem{p2pSurvey} A. Passarella, A survey on content-centric technologies for the current Internet: CDN and P2P solutions

\bibitem{BTSyncFAQ} http://www.bittorrent.com/help/faq/sync
\bibitem{btsynctech} http://www.bittorrent.com/sync/technology
\bibitem{btsyncuserguide} http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf
\bibitem{btsyncapi} http://www.bittorrent.com/sync/developers/api

\bibitem{cryptoDef} Rivest, Ronald L. (1990). "Cryptology". In J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{bittorrentDHT} http://www.bittorrent.org/beps/bep\_0005.html
\bibitem{bittorrentProtocol} http://www.bittorrent.org/beps/bep\_0003.html
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". https://tools.ietf.org/html/rfc3164, August 2001.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". https://tools.ietf.org/html/rfc5424, March 2009.
\bibitem{skypeSupernode} S. Guha, N. Daswani, R. Jain, "An Experimental Study of the Skype Peer-to-Peer VoIP System". http://saikat.guha.cc/pub/iptps06-skype/ .

>>>>

@@

% TODO make title page look nicer
\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[1.75cm]
\LARGE{\textsc {\textbf{Improving the Speed of Peer to Peer Backup Systems with BitTorrent}}}\\[0.5cm]
\vspace{0.25cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.75cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.75cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1.5cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
% TODO adjectives
% TODO format this section better
Mih\'aly H\'eder, our on-site Project Advisor, for his advice, insight, expertise, and bottomless teapot.\\

\noindent G\'abor S\'ark\"ozy, our off-site Project Advisor, for his guidance, encouragement, and editorial skills. \\

@@

Although they have not gained much popularity, peer to peer (P2P) file backup systems have been created and studied by researchers for over a decade. These systems do not suffer from the aforementioned drawbacks of centralized systems; they are free to use, limited in storage only by the user, and do not require a trusted central entity. Instead of backing up their data to a server, peers back up their data to \textit{each other}. However, abandoning the centralized server model in favor of a distributed one brings with it new problems that must be addressed before wide-spread adoption can be expected. Research in this area has focused on topics such as handling node churn \cite{ChurnResilient}, efficient routing algorithms \cite{Kademlia}, and minimizing bandwidth \cite{PeerStore}.

We have designed and implemented a new P2P backup system, called \mbox{BTBackup}, that improves the speed of backing up and recovering data. Our main contribution, and the technology responsible for faster file backup and recovery, is the way in which we handle data transfer: BitTorrent Sync, a new synchronization application created by BitTorrent, Inc. BitTorrent Sync uses a modified version of the BitTorrent protocol \cite{BTSyncFAQ} in order to quickly synchronize files between groups of peers. This protocol is especially effective at transferring large files, which makes its use perfect for the domain of P2P file backup. By leveraging BitTorrent Sync, we take advantage of BitTorrent's ability to better utilize a peer's bandwidth by downloading from multiple sources at once. This is in contrast to other P2P backup systems, which directly download from one source at a time. Our approach takes advantage of the fact that P2P backup systems require data replication, the act of inserting several redundant copies of data into the network, to combat node churn. We view the set of nodes storing replications for a given file as a BitTorrent swarm, allowing us to use the BitTorrent protocol without additional overhead.

We created test scenarios to (1) measure the extent to which it increases data backup and recovery transfer speeds, and (2) ensure our system is a feasible backup solution under realistic conditions. To test the former, we measured the rates of data transfer over time when backing up 1 GB of data. In order to see the effects filesize has on speed, we ran this test thrice: once with one 1GB file, once with ten 100MB files, and once with one hundred 10MB files. To test the latter, we created a test scenario that simulated usage of our system in a realistic environment. Each instance of this scenario created 100 peers on a network using MTA SZTAKI's cloud computing environment: SZTAKI Cloud. Specifically, this scenario measured the effects of node churn, or the rate at which nodes enter and leave the network, on our system. Since our system handles churn by moving replicas from unavailable nodes to available ones, we measure how much extra network traffic is generated to see the effects of churn. We take this measurement by running a test instance with no churn, and then running another one with churn. To provide a realistic setting, we had each peer limit their download and upload speeds to values that are based off of worldwide Internet bandwidth statistics.

After running our tests, we found that BitTorrent performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that larger but fewer files are handled more efficiently than a greater number of smaller files, given the same amount of total data. We also determined that our system handles node churn well, when the rate of churn is modeled off of the average Internet user. Our final and most important result is that our system was able to achieve data transfer rates up to \~300\% quicker than the rates that could be realistically achieved in traditional backup systems.

@@

\subsection{Peer to Peer Networks}

@@

\subsection{Fairness} \label{sec:Fairness_chap:Background}
Another aspect of P2P backup systems is fairness between peers. Peers need to be storing an amount of data proportional to the amount that they are backing up to other peers. This can be challenging to enforce, because untrustworthy peers can attempt to game the system to obtain free backup storage. For example, consider a simple system where each peer must offer to store the same amount of data that they back up on other peers. A peer could claim that all of the storage space that it should be offering is being used by other peers, while in reality the peer has not taken in any other peer's data. It is clear that a mechanism needs to be built into the system that ensures that peers store the data of each other.

@@

For every file a peer wishes to back up, it must find a predetermined number of nodes that can store the file. To ensure an even distribution of responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated; the DHT provides the functionality to find the node whose ID is \textit{closest} to the randomly generated bitstring, for the overlay network's given definition of closeness. For example, Kademlia, the DHT that the BitTorrent application bases its DHT implementation on, uses XOR operations to find closest IDs \cite{kademliaDHT}. With Kademilia, the distance $d(x,y)$ between nodes with IDs $x$ and $y$ is defined as:

$$
d(x,y)=x \oplus y
$$

% TODO: Double-check that logn is correct.
To provide $O(\log n)$ lookup times, the DHT is arranged as a binary tree, where each node is a leaf and the path to a node is the bits of its ID. The binary tree is further partitioned into subtrees. In order for any given node $m$ to find any other node $n$, $m$ must know the location of node $o$, which is a part of $n$'s subtree. In this way, all nodes must know about at least one node in each subtree.

Once the peer has found the node it is looking for, it can query it for the candidate node's metadata record. From the metadata record, the peer can calculate if the candidate node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in Section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the candidate node does not have too many blacklisters. If the candidate node meets both requirements, the peer chooses it to store a replica and uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

\section{Fairness} \label{sec:Fairness_chap:BTBackup}
% TODO we say "if n backups", but also refer to each backup as a "replica". we should be consistent. where else do we do this? ctrl-f replica
To ensure fairness (see Section \ref{sec:Fairness_chap:Background} for background information), each node must contribute storage space proportional to the amount that they are backing up. Since a peer will have replicas of its file stored on multiple nodes, the amount of space that a peer offers\footnote{That is, offers to store when it assumes the role of a node.} must be much larger than the amount of unique data that it is backing up. If $n$ backups are maintained for each file and $\mathcal{F}$ represents the set of files that a peer backs up, the total amount of space $t$ that the peer must offer can be expressed as:
\begin{equation}
t=n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i)
\end{equation}
There exists one problem with this mechanism: when the network first starts up, no peer has created any backups, so no one is obligated to store data for other peers. To solve this, our system requires that each peer is obligated to take at least $s$ bytes of data from other peers, regardless of how much data it has backed up. To include this, $t$ can be reexpressed as:
\begin{equation}
t=max(s,n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i))
\end{equation}
Let $a$ be the amount of data a node is currently storing, and $z$ be the size of a file a peer is trying to back up. When the peer finds a candidate node with $t - a > z$, it can choose that node as a replication site, knowing that it is obligated to accept the data.

@@

In this scenario, we tested how our system handles a constant amount of data spread out across a varying number of files. We run this test for three reasons. First, it allows us to test the capabilities of BitTorrent Sync in handling a large number of backups. From the data gathered here, it is possible to determine how well BitTorrent Sync would scale for use in a production system, where thousands of users could each be backing up thousands of files of varying sizes. Second, it allows us to measure the performance of BitTorrent against different file sizes. Since the use case for BitTorrent is typically downloading large files, it is important to determine whether or not our system will perform well when users try to backup many small files, should it be used in a production environment. Third, it will demonstrate the ability of our system to backup and recover files faster than if they were transferred by a direct download protocol.

@@

@@

\subsection{Entities Backing Up a 1 GB File} \label{subsec:EntitiesBackingUpa1GBFile}

@@

As with \ref{fig:NodeRecoverySpeed}, we believe the interval of time at the start of the test with no activity is due to BitTorrent Sync indexing the 1 GB file before it can transfer it.

\section{Effects of Churn} \label{sec:EffectsofChurn_chap:Results}

@@

Section \ref{subsec:EntitiesBackingUpa1GBFile} showed that our system lessens the Peer's load of backing up a file by distributing the task to the nodes as well. This has the side effect of speeding up the backup process, because nodes upload the data they have at a given time to each other, better utilizing their download bandwidth. It is important to consider the number of replicas per file here, because the replica count that is maintained affects the speed and bandwidth usage of the backup and restore procedures. As the number of replicas per file increases, more traffic must be generated to create and maintain those replicas, but the download speed when recovering will be greatly improved. Of course, the maximum recovery speed is limited by the peer's download bandwidth.

Section \ref{sec:EffectsofChurn_chap:Results} explained that, in the presence of an average amount of churn, the average peer would need to make a new replica of any given file every 11 days. This time interval is derived by taking the average amount of time between the creation of replicas in our test instance and scaling that number based on the scaling factor that we used for the entire test instance.

@@

To test whether or not our system provided an increase in file transfer speeds, in addition to providing solutions for the other challenges of P2P backup systems, we implemented a simplified version of our system and tested it on MTA SZTAKI's cloud computing system. We found that it was able to handle node churn with a reasonable amount of overhead in network traffic. More importantly, however, we found that our system allowed for a \~300\% improvement in file backup and restoration speeds. This would not be possible if these data transfers were only between a user and some other entity, whether it is the service provider in a centralized backup system or a single peer in another P2P backup system.

@@

\subsection{Incentivizing Uptime}

As mentioned in Section \ref{sec:EffectsofChurn_chap:Results}, our system could see much lower replication rates if the average uptime per peer is longer. In order to help increase the average, the fairness mechanism described in Section \ref{sec:Fairness_chap:BTBackup} could be extended to offer an incentive for having high uptimes. When a peer stays online for a long time, it could be awarded more space to backup data. This could increase the likelihood that users keep their machines online for longer periods of time, since it essentials gives them free storage. However, if a system like this were to be implemented, there are several problems that need to be addressed. If some users are getting more storage space than what they are offering, that means that some users would be getting less space than what they are offering. Our system would not only need to determine who gets less storage space, but also what to do if many users are staying online often; it is possible that most people do this, so there is not much extra storage space to offer. In addition to this, we would need to figure out when to revoke extra space, in case malicious nodes attempt to game the system and limit their availability after being awarded space. If this is the case, more decisions need to be made in order to determine which replicas will be removed from the system, if the peer is using some or all of the space that is being revoked.

@@

\bibitem{dropboxusers} https://www.dropbox.com/news/company-info
\bibitem{oneddriveusers} http://blog.onedrive.com/over-250m-people-using-skydrive/
\bibitem{ChurnResilient} S. Legtchenko, S. Monnet, P. Sens, G. Muller, Churn-Resilient Replication Strategy for Peer-to-Peer Distributed Hash-Tables
\bibitem{Kademlia} P. Maymounkov, D. Mazi\`eres, Kademlia: A Peer-to-Peer Information System Based on the XOR Metric
\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, pStore: A Secure Peer-to-Peer Backup System
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan, PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan, Storage and Search in Dynamic Peer-to-Peer Networks
\bibitem{p2pSurvey} A. Passarella, A survey on content-centric technologies for the current Internet: CDN and P2P solutions
\bibitem{BTSyncFAQ} http://www.bittorrent.com/help/faq/sync
\bibitem{btsynctech} http://www.bittorrent.com/sync/technology
\bibitem{btsyncuserguide} http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf
\bibitem{btsyncapi} http://www.bittorrent.com/sync/developers/api
\bibitem{cryptoDef} Rivest, Ronald L. (1990). "Cryptology". In J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{bittorrentDHT} http://www.bittorrent.org/beps/bep\_0005.html
\bibitem{bittorrentProtocol} http://www.bittorrent.org/beps/bep\_0003.html
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". https://tools.ietf.org/html/rfc3164, August 2001.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". https://tools.ietf.org/html/rfc5424, March 2009.
\bibitem{skypeSupernode} S. Guha, N. Daswani, R. Jain, "An Experimental Study of the Skype Peer-to-Peer VoIP System". http://saikat.guha.cc/pub/iptps06-skype/ .
\bibitem{kademliaDHT} P. Maymounkov, D. Mazi\`eres, Kademlia: A Peer-to-peer Information System Based on the XOR Metric, IPTPS '01 Revised Papers from the First International Workshop on Peer-to-Peer Systems (2002), 53-65.
